Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-18 analysis/paper/paper.Rmd
Figure edits

pos = position_dodge(width=0.3)
all_est %>%

@@

  ggplot(aes(x = model,
             y = N,
             #color = model
             )) +
  geom_errorbar(aes(ymin = Lci,ymax = Uci, group=event_name), position = pos, width=0) + 
  geom_point(aes(shape = event_name, color = census), position = pos, size = 4) +
    #facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_shape_manual(values = c(21, 19), name="Event") +
  scale_color_manual(values = c("grey35", "darkred"), name="Census type") +
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #scale_size(guide = "none")+
  theme(legend.position="top",legend.key = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.50, "cm"),
        #axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 11, color = "black"),
        axis.text.y = element_text(size = 11, color = "black"),
        strip.text.x = element_text(size = 11,color = "black"))
  #scale_color_brewer(palette = "Dark2")

@@

```{r length-freq-p, fig.cap = "Length frequency histogram of Northern Pikeminnow caught using hook-and-line angling during the study."}
length_freq_p = gastric_df %>%
  ggplot(aes(length)) +
  geom_histogram(breaks = seq(150, 650, by = 50),
                 col = "black",
                 fill = "gray30",
                 alpha = .2) +
  labs(x = "Total Length (mm)",
       y = "Frequency") +
  xlim(c(100, 700)) +
  ylim(c(0, 800)) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  scale_y_continuous(breaks = seq(0, 550, by = 50)) +
  theme(axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black",
                                   vjust = 3)) +
  theme_classic()

@@

pFish = bio_results %>%
  ggplot(aes(ymd, f50_g)) +
  geom_line(size = 1.15) +
  geom_ribbon(data = bio_results,
              aes(ymd,
                  ymin = f10_g,
                  ymax = f90_g),
              color = "grey65",
              alpha = 0.4) +
  theme_bw() +
  labs(y = "Fish consumed (g)",
       x = "",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, -.3, .2), "cm"))

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temp"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, .1, .1), "cm"))

@@

```{r adult-imp-p, fig.cap = "The estimated number of DSR (fall) and NRR (spring) emigrants consumed by Northern Pikeminnow in Deadwater Slough (top panel) across a range of diet scenarios where 10-90% of the diet consists of juvenile Chinook salmon. The bottom panel provides the adult equivalents assuming a Lower Granite Dam smolt-to-adult rate (SAR) from McCann et al. 2019."}
impact_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet, p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),
                   sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  bind_rows(impact_df %>%
              select(season,
                     perc_diet,
                     p_chnk,
                     N = adult_N,
                     Lci = adult_Lci,
                     Uci = adult_Uci) %>%
              group_by(perc_diet, p_chnk) %>%
              summarise(across(c("N", "Lci", "Uci"),
                   sum),
             .groups = "drop") %>%
             mutate(Stage = "Adult Equivalents")) %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  filter(perc_chnk %in% c(10, 30, 50)) %>%
  ggplot(aes(x = perc_diet,
             y = N,
             color = as.factor(perc_diet))) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  geom_point(size = 3) +
  facet_grid(vars(Stage),
             vars(perc_chnk),
             scales = "free_y") +
  scale_color_viridis_d(name = "Percent\nFish in Diet") +
  scale_y_continuous(labels = scales::comma) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        strip.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black")) +
  labs(y = "Number Chinook Consumed")

>>>>

pos = position_dodge(width=0.3)
pm_est_labels <- c("Chapman","Schnabel","Schnabel \n Delayed-mixing")
all_est %>%

@@

  ggplot(aes(x = model,
             y = N,
             #color = model
             )) +
  geom_errorbar(aes(ymin = Lci,ymax = Uci, group=event_name), position = pos, width=0) + 
  geom_point(aes(shape = event_name), position = pos, size = 4) +
    #facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_shape_manual(values = c(21, 19), name="Event") +
  #scale_color_manual(values = c("grey35", "darkred"), name="Census type") +
  scale_x_discrete(labels=c(pm_est_labels))+
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #scale_size(guide = "none")+
  theme(legend.position = c(.15, .85),legend.background = element_blank(),
        legend.key.size = unit(.5, "cm"),legend.box = 'horizontal',
        #axis.title.x = element_blank(),
        axis.text.x = element_text(size = 11, color = "black"),
        axis.text.y = element_text(size = 11, color = "black"),
        strip.text.x = element_text(size = 11,color = "black"))
  #scale_color_brewer(palette = "Dark2")

@@

```{r length-freq-p, fig.cap = "Length frequency histogram of Northern Pikeminnow caught using hook-and-line angling during the study."}
length_freq_p = gastric_df %>%
  ggplot(aes(length)) +
  geom_histogram(breaks = seq(150, 650, by = 50),
                 col = "black",
                 fill = "gray30",
                 alpha = .2) +
  labs(x = "Total Length (mm)",
       y = "Number of Northern Pikeminnow") +
  xlim(c(100, 700)) +
  ylim(c(0, 800)) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  scale_y_continuous(breaks = seq(0, 550, by = 50)) +
  theme(axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"))

@@

pFish = bio_results %>%
  ggplot(aes(ymd, f50_g)) +
  geom_line(size = 1.1) +
  geom_ribbon(data = bio_results,
              aes(ymd,ymin = f10_g,
                  ymax = f90_g),
              color = "grey55",
              alpha = 0.4) +  theme_bw() +
  labs(y = "Fish consumed (g)",
       x = "", title = "") +
  facet_rep_wrap(~season,scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, -.3, .2), "cm"))

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temp"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.2, .3, .1, .1), "cm"))

@@

```{r adult-imp-p, fig.cap = "The estimated number of DSR (fall) and NRR (spring) emigrants consumed by Northern Pikeminnow in Deadwater Slough (top panel) across a range of diet scenarios where 10-90% of the diet consists of juvenile Chinook salmon. The bottom panel provides the adult equivalents assuming a Lower Granite Dam smolt-to-adult rate (SAR) from McCann et al. 2019."}
#impact_p = impact_df %>%
#  select(season,
#         perc_diet,
#         p_chnk,
#         N = juv_N,
#         Lci = juv_Lci,
#         Uci = juv_Uci) %>%
#  group_by(perc_diet, p_chnk) %>%
#  summarise(across(c("N", "Lci", "Uci"),sum),
#            .groups = "drop") %>%
#  mutate(Stage = "Juveniles") %>%
#  bind_rows(impact_df %>%
#              select(season,
#                     perc_diet,
#                     p_chnk,
#                     N = adult_N,
#                     Lci = adult_Lci,
#                     Uci = adult_Uci) %>%
#              group_by(perc_diet, p_chnk) %>%
#              summarise(across(c("N", "Lci", "Uci"),
#                   sum),
#             .groups = "drop") %>%
#             mutate(Stage = "Adult Equivalents")) %>%
#  mutate(p_chnk = p_chnk * 100) %>%
#  rename(perc_chnk = p_chnk) %>%
#  filter(perc_chnk %in% c(10, 30, 50)) %>%
#  ggplot(aes(x = perc_diet,y = N)) +
#  geom_errorbar(aes(ymin = Lci,
#                    ymax = Uci),
#                width = 0.1) +
#  geom_point(size = 3) +
#  facet_grid(vars(Stage),
#             vars(perc_chnk),
#             scales = "free_y") +
#  scale_color_viridis_d(name = "Percent\nFish in Diet") +
#  scale_y_continuous(labels = scales::comma) +
#  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
#  theme(#axis.text.x = element_blank(),
        #legend.position = "bottom",
        #axis.title.x = element_blank(),
        #axis.ticks.x = element_blank(),
#        axis.text.y = element_text(size = 11,
#                                   color = "black"),
#        strip.text.x = element_text(size = 11,
#                                    color = "black"),
#        strip.text.y = element_text(size = 11,
#                                    color = "black")) +
#  labs(y = "Number Chinook Consumed")

#impact_p

impact_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet, p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  filter(perc_chnk %in% c(10, 30, 50)) %>%
  ggplot(aes(x = perc_diet,y = N, group=as.factor(perc_chnk), color=as.factor(perc_chnk))) +
  geom_point(size = 2) + geom_line(size = 1.05)+
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name="Proportion Chinook", values=c("lightsteelblue","steelblue3","navyblue"))+
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.15, .85),legend.background = element_blank(),
        legend.key.size = unit(.5, "cm"),legend.box = 'horizontal') +
  labs(y = "Estimated Chinook Consumed", x="Percent Fish in Pikeminnow Diet")
